Experiment 2

### 2021-06-29 experiments/experiment 2/experiment 2.Rmd
improved experiment framework

---
title: "Experiment 1"
author: "Owen Petchey"
date: "6/25/2021"
output: html_document
---

@@

```{r}
num_CB_strains <- 9
num_SB_strains <- 9
num_PB_strains <- 9
CB_var_range <- 0.015789474
CB_var_TO <- -5
SB_var_range <- 0.010
SB_var_TO <- -20.5
PB_var_range <- 0.010
PB_var_TO <- -20.5

@@

CBtraits <- var_expt$pars[[num_div_treatment_levels]]$CB
P <- 1 #10^seq(-5, 5, 0.1)
SR <- 10^seq(0, 3, 0.1)
gr_rateCB1 <- growth1(P, CBtraits$g_max_CB[1], CBtraits$k_CB_P[1]) * inhibition(SR, CBtraits$h_SR_CB[1])
gr_rateCB9 <- growth1(P, CBtraits$g_max_CB[num_CB_strains], CBtraits$k_CB_P[num_CB_strains]) * inhibition(SR, CBtraits$h_SR_CB[num_CB_strains])

CB_TO1 <- ggplot() +
  geom_point(aes(x = CBtraits$h_SR_CB, y = CBtraits$g_max_CB))
CB_TO2 <- ggplot() +
  geom_line(aes( x = log10(SR), y = gr_rateCB1)) +
  geom_line(aes( x = log10(SR), y = gr_rateCB9), col = "blue")

SBtraits <- var_expt$pars[[num_div_treatment_levels]]$SB
P <- 1 #10^seq(-5, 5, 0.1)
SO <- 1
O <- 10^seq(-2.5, 2.5, 0.1)
gr_rateSB1 <- growth2(P, SO, SBtraits$g_max_SB[1], SBtraits$k_SB_P[1], SBtraits$k_SB_SO[1]) *
  inhibition(O, SBtraits$h_O_SB[1])
gr_rateSB9 <- growth2(P, SO, SBtraits$g_max_SB[9], SBtraits$k_SB_P[9], SBtraits$k_SB_SO[9]) *
  inhibition(O, SBtraits$h_O_SB[9])

SB_TO1 <- ggplot() +
  geom_point(aes(x = SBtraits$h_O_SB, y = SBtraits$g_max_SB))
SB_TO2 <- ggplot() +
  geom_line(aes( x = log10(O), y = gr_rateSB1)) +
  geom_line(aes( x = log10(O), y = gr_rateSB9), col = "blue")

PBtraits <- var_expt$pars[[num_div_treatment_levels]]$PB
P <- 1 #10^seq(-5, 5, 0.1)
SO <- 1
O <- 10^seq(-2.5, 2.5, 0.1)
gr_ratePB1 <- growth2(P, SO, PBtraits$g_max_PB[1], PBtraits$k_PB_P[1], PBtraits$k_PB_SR[1]) *
  inhibition(O, PBtraits$h_O_PB[1])
gr_ratePB9 <- growth2(P, SO, PBtraits$g_max_PB[9], PBtraits$k_PB_P[9], PBtraits$k_PB_SR[9]) *
  inhibition(O, PBtraits$h_O_PB[9])

PB_TO1 <- ggplot() +
  geom_point(aes(x = PBtraits$h_O_PB, y = PBtraits$g_max_PB))
PB_TO2 <- ggplot() +
  geom_line(aes( x = log10(O), y = gr_ratePB1)) +
  geom_line(aes( x = log10(O), y = gr_ratePB9), col = "blue")

(CB_TO1 + SB_TO1 + PB_TO1) / (CB_TO2 + SB_TO2 + PB_TO2)
```

@@

```{r}
default_sim_duration <- 100000
```

```{r}
default_minimum_abundances <- rep(1000, 3)
names(default_minimum_abundances) <- c("CB", "PB", "SB") 
```

```{r}
sim_number <- 1
default_log10a_series <- c(-1, -6, -1)
initial_state <- new_initial_state(num_CB_strains,
                                   num_PB_strains,
                                   num_SB_strains,
                                   values = "bush_ssfig3")
initial_state[grep("CB_", names(initial_state))] <- 10/num_CB_strains
sim_res_novar <- run_simulation(parameter_values = var_expt$pars[[sim_number]],
                          initial_state = initial_state)
plot_dynamics(sim_res_novar)
#ggsave(here("simulations/expt2/figures/switching_novar.pdf"), width = 10)
```

@@

@@

soi <- "O"
ggplot() +
  geom_path(data = filter(tmp_novar,functional_group == soi),
            aes(x=a, y = log10(Total_quantity), group = direction)) +
  geom_path(data = filter(tmp_highvar,functional_group == soi),
            aes(x=a, y = log10(Total_quantity), group = direction),
            linetype = "dashed", lwd=2, col="red") +
  ggtitle("Solid line is with no intraspecific diversity.\nDashed line is with intraspecific diversity")
##ggsave(here("simulations/figures/switching_comparison.pdf"), width = 5, height = 4)

@@

```{r}
var_expt <- run_ss_var_experiment()
```

@@

>>>>

---
title: "Experiment 2"
author: "Owen Petchey"
date: "6/25/2021"
output: 
  html_document: 
    keep_md: yes
---

@@

```{r}
num_CB_strains <- 9
num_SB_strains <- 9
num_PB_strains <- 9
CB_var_range <- 0.015789474
CB_var_TO <- -5
SB_var_range <- 0.0015789474
SB_var_TO <- -20.5
PB_var_range <- 0.0015789474
PB_var_TO <- -20.5

@@

```{r}
display_diversity()
```

@@

```{r}
default_sim_duration <- 1000000
```

```{r}
default_minimum_abundances <- rep(100, 3)
names(default_minimum_abundances) <- c("CB", "PB", "SB") 
```

```{r}
sim_number1 <- 1
default_log10a_series <- c(-1, -8, -1)
initial_state <- new_initial_state(num_CB_strains,
                                   num_PB_strains,
                                   num_SB_strains,
                                   values = "bush_ssfig3")
initial_state[grep("CB_", names(initial_state))] <- 10/num_CB_strains
sim_res_novar <- run_simulation(parameter_values = var_expt$pars[[sim_number1]],
                          initial_state = initial_state)
plot_dynamics(sim_res_novar)
##ggsave(here("simulations/expt2/figures/switching_novar.pdf"), width = 10)
```

@@

```{r}
sim_number2 <- 2
sim_res_highvar <- run_simulation(parameter_values = var_expt$pars[[sim_number2]],
                          initial_state = initial_state)
plot_dynamics(sim_res_highvar)
##ggsave(here("expteriment 2/figures/switching_highvar.pdf"), width = 10)

@@

soi <- "O"
ggplot() +
  geom_path(data = filter(tmp_novar,functional_group == soi),
            aes(x=a, y = log10(Total_quantity), group = direction)) +
  geom_path(data = filter(tmp_highvar,functional_group == soi),
            aes(x=a, y = log10(Total_quantity), group = direction),
            linetype = "dashed", lwd=2, col="red") +
  ggtitle("Solid line is with no intraspecific diversity.\nDashed line is with intraspecific diversity")
##ggsave(here("experiment 2/figures/switching_comparison.pdf"), width = 8, height = 10)

@@

```{r}
var_expt <- run_ss_var_experiment()
saveRDS(var_expt, here("experiments/experiment 2/data/ss_data.RDS"))
```

@@

ss_result1 <- var_expt[result_index1,]$ss_res[[1]]
ss_result2 <- var_expt[result_index2,]$ss_res[[1]]
xlims = c(-7, -1)
```
